---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# but

<!-- badges: start -->
<!-- badges: end -->

The goal of but is to allow users to easily edit existing functions to suit their specific needs.
Edit the formals of a function and apply additional processing to its inputs and output.

## Installation

You can install the development version of but from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("hrryt/but")
```

## Examples

```{r}
library(but)
```

Use named arguments to change the default values of a function.
```{r}
max_rm <- max |> but(na.rm = TRUE)
max_rm(0, NA, 2, 1)
```

`but()` can act on calls as well as functions.

Use unnamed arguments to preprocess inputs.
```{r}
(x <- log(c(0, NA, 1)))
min(x)
min(x) |> but(if(-Inf %in% c(...)) return(-Inf))
min_inf <- min |> but(if(-Inf %in% c(...)) return(-Inf))
min_inf(x)
```

Reference `.out` to modify the output of a function.

Use `on.exit()` to clean up after a function call.
```{r}
(strsplit1 <- strsplit |> but(.out[[1]]))
strsplit1("a.b.c", ".", fixed = TRUE)
read.csv |> but(stringsAsFactors = TRUE, on.exit(unlink(file)))
```

Make `data` the first argument of `lm()` so it can be piped in.
```{r}
args(lm)
lm4pipe <- lm |> but(data = , .first = TRUE, .wrap = FALSE)
args(lm4pipe)
mtcars |> subset(cyl == 4) |> lm4pipe(mpg ~ disp)
```

Specify exactly what the call to `lm()` should look like with `:=`.

This process supports data masking with `rlang`.
```{r}
resample <- function(x) x[sample(nrow(x), replace = TRUE), , drop = FALSE]
lm_resample <- lm |> but(data := resample({{data}}), .nse = TRUE)
lm_resample(mpg ~ disp, subset(mtcars, cyl == 4))$call

lm4pipe_resample <- lm |> but(
  data = , .first = TRUE, .nse = TRUE,
  data := resampled_data, resampled_data <- resample(data)
)
mtcars |> subset(cyl == 4) |> lm4pipe_resample(mpg ~ disp)
```

Change the default value of `drop` in `[`.
```{r}
(m <- diag(4))
m[2, ]
`[` <- `[` |> but(drop = FALSE, .store = TRUE)
m[2, ]
m[2, , drop = TRUE]
rm(`[`)
```

Remove unwanted arguments with `.rm`.

Modify the call directly with `:=`.
```{r}
(square <- matrix |> but(nrow = sqrt(length(data)), ncol = .rm, ncol := nrow))
square(1:9, byrow = TRUE)
```

See `?but` for more information and examples.
